---
title: "FlightScanner: Find the best flight for you!"
output: 
    rmarkdown::html_vignette:
       
author: Yang Qiao, Dapeng Hu, Min Zhang, Xin Zhang and Zerui Zhang
date: "5/7/2019"
vignette: >
  %\VignetteIndexEntry{FlightScanner}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction

Finding the cheapest flight from point A to point B could be a headache for many of us, especially with other multiple constraints, such as duration, departure and arrival time, layover, etc. The goal of the `FlightScanner` package is to provide a simple and straightforward interface for interacting with [Rapid API--Sky Scanner](https://rapidapi.com/skyscanner/api/skyscanner-flight-search) through R. The Sky Scanner API lets users to search for flight and query flight prices from Skyscanners database, as well as quotes from ticketing agencies.  Besides these basic functionalities as a flight searching tool, `FlightScanner` allows users to schedule searches and record results antomatically. The package also provides a Shiny APP to visualize the trip and to show the available ticket options according to the customized constraints. 


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Getting Started

(introdue how to install our package and the api our package based on)

```{r}
library(flightscanner)
```

(introduce the dataset Airport in our package and show some plots and tables)

## Setup function 1: keychecking.R

## Setup function 1: setAPI.R

# Main Functions

## Download data with API

## Data Storage

## Data Processing 

# Automatical Download Data



